---
title: "Étapes clusters analysis (future)"
author: "Me"
format: html
editor: visual
---

## Goal

1.  See if we can get satisfactory grouping
2.  Select the most interesting cluster and explore the observations
3.  Keep the model for prediction of further data collection
4.  Descriptive analysis of the cluster to detect other patterns
    1.  Assess the usefulness of
        1.  Tags/labels
        2.  Rank
        3.  Demo and others
    2.  Find a way to use information from the observations to link to new data collection strategy
5.  Think of other in depth analysis for a mixed model prediction
    1.  Other level of observation based on the clusters/observation for instance

## Libraries and loading the data

```{r}
pacman::p_load(tidyverse, rvest, tidySEM, tictoc, FactoMineR, factoextra, corrplot, lsa)

# Options ----
theme_set(theme_bw())

# Data ----
df <- read_rds("data/df.rds")
```

## Preparing the data for the PCA

-   Data cleaning

-   Keep numerical variable

-   No need for id variable (just keep a copy of the original data with all the variables)

```{r}
# Keep only continuous variables
df_pca <- 
  df %>% 
  select(hp:res)
```

## Performing the PCA

Do the dims sum up to 70% at least withour going beyond 5?

-   Yes: Keep going

-   No: Need data selection? data transformation? more data? CA? Keep going?

Do I see a pattern/cluster in the ind plot?

-   Yes: Good promising

-   No: Let's dive in anyway

```{r}
res_pca <- PCA(df_pca, 
           ncp = 5 # number of dim to retain: default to 5
           )
```

## PCA diagnostic

### How many dimensions?

-   How many dim to retain (preferably max 5)?

    -   If removing is necessary, go to `PCA()` and change the ncp argument

```{r}
# Eigenvalue
fviz_screeplot(res_pca, addlabels = TRUE)
```

### Variables importance (contribution)

-   Observe wich variables (tags/labels) should be considered in the future (can be useful for modelling, mixed model) by removing poorly informative variable or using bayesian inference

```{r}
fviz_contrib(res_pca, choice = "var", 
             axes = 1:3 # Chose how many dimensino to considerate
             )
```

## PCA dimensions names

-   Give sensical names

-   Remove unecessary dimension (if filled by NAs for instance)

    -   If so, go to `PCA()` and change the ncp argument

```{r}
# Correlation plot
res_pca$var$cor %>% 
  corrplot()

# Top 5 positive/negative correlated variables by dim
apply(res_pca$var$cor, 
      MARGIN = 2, 
      FUN = function(x) sort(x[x >=0.7 | x <= -0.7], decreasing = T)[1:5], 
      simplify = FALSE)
```

## Performing HCPC

-   Check if the clustering make visual sens (not to much overlap)

-   Test with higher or smaller values to see if it make more visual sens (less overlap)

```{r}
res_hcpc <- HCPC(res_pca,
                 nb.clust = -1, # Automatic number of cluster
                 nb.par = 5, # Top 5 most representative per cluster (see bellow)
                 order = TRUE, # Order cluster based on the first dim
                 graph = FALSE # No graph from here
                 )

# Visualization
fviz_cluster(res_hcpc) +
  theme_bw()
```

## HCPC diagnostic

### Description of the clusters by the variables

-   Keep variables with low p-values (\< 0.05)

-   Note: v.test alow a quick glimpse

    -   \>0: cluster mean higher than overall mean

    -   \<0: cluster mean lower than overall mean

-   Try to give a name to each category or at least keep in mind their peculiarity

    -   If to complicated, look with dimension bellow

```{r}
# Description of the clusters by the variables
res_hcpc$desc.var
```

### Description of the cluster by the dimension

-   Same as before, see if it makes more sens here

-   If there is still some difficulties naming the cluster, look at the individuals bellow

```{r}
# Description of the cluster by the dimension
res_hcpc$desc.axes

```

### Description of the clusters by the individuals

-   Get information about these individuals and why they are relevant (especialy those from Paragon)

    -   See next part for that

-   Can help naming the category

-   Check if we already have important individuals, it can help targeting the right clusters

```{r}
# Description of the cluster by the individuals
  # Paragon: Most representative individuals of the cluster (closer to the center)
  # Dist: Less representative individuals of the cluster (farther to the center)
  # NOTE: the lower value = closer, bigger value = further
res_hcpc$desc.ind

```

### Get representative individuals for each cluster

-   Same as before

```{r}
# HCPC dataframe with the clusters for each ind
df_hcpc <- 
  res_hcpc$data.clust %>% 
  select(clust) %>% 
  bind_cols(df)

# Get representative individual for each cluster
list_rep <- 
  map(res_hcpc$desc.ind$para, names) %>% 
  flatten_chr()

# Filter the representative members
df_hcpc %>% 
  filter(row_number() %in% list_rep) %>% 
  arrange(clust)

```

## HCPC targeting cluster

-   Find which cluster(s) contains the most important individuals to have a first glimpse of the most important clusters

-   Do back and forth between the cluster graph and this result to have an idea how close are this VIPs to each other (more detailed analysis bellow)

```{r}
list_vip <- c(1, 54, 62, 100, 147)

df_hcpc %>% 
  filter(row_number() %in% list_vip) %>% 
  arrange(clust)

```

## Distance between les VIPs

### Most similar profiles

-   Can give further indication if the clusters are good (and by definition the data)

    -   If the data is not good: Transformation?

-   Can give information if the cluster should have more/less group

```{r}
# Ind coord
ind_coord <- res_pca$ind$coord

# Sim matrix
matrix_sim <- 
  ind_coord %>% 
  t() %>% 
  cosine()

# Similarity among the VIPs
  # NOTE: Similarity is really close to correlation and range from -1 to 1
matrix_sim[list_vip, list_vip] %>% 
  corrplot::corrplot(order = "hclust", # To create clusters
                     addrect = 3 # Number of clusters
                     )

```

### Further profiling (if needed)

-   Investigate the 4 or 9 closest profile to the VIPs

-   If the clusters still do not make sens, create new cluster based on the VIP closest ind

    -   It can be the beginning of further mixed model analysis by comparing these new clusters

```{r}
# The 10 closest inds of ind 7
matrix_sim %>% 
  .[7,] %>% 
  sort(decreasing = T) %>% 
  .[2:11]

# Proximity between 7 and 77
cosine(ind_coord[7,], ind_coord[77,])

# Proximity between 7 and 10, 100 and 1000
matrix_sim %>% 
  .[7,] %>% 
  .[c(10, 100, 1000)]
```

### Most influencial individuals

```{r}
res_pca$ind$contrib %>% 
  rowSums() %>% 
  sort(decreasing = T) %>% 
  .[1:10]
```

```{r}
library(plotly)
p1 <- 
  df_hcpc %>%
  mutate(clust = factor(clust)) %>% 
  summarise(total = mean(total),
            .by = clust) %>% 
  ggplot(aes(clust, total)) +
  geom_col(fill = "cyan", alpha = 0.4, color = "black")+
  geom_label(aes(label = round(total, 1)))

plotly::ggplotly(p1)
```
